---
title: "CytometryQC"
date: "`r BiocStyle::doc_date()`"
author:
- name: David Rach
  email: drach@som.umaryland.edu
  affiliation: University of Maryland, Baltimore
package: "`r BiocStyle::pkg_ver('CytometryQC')`"
resource_files:
  - images
output:
  BiocStyle::html_document
vignette: |
  %\VignetteIndexEntry{CytometryQC}
  %\VignettePackage{CytometryQC}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Our end goal is to enable everyone to rapidly set up their own initial [InstrumentQC](https://umgccfcss.github.io/InstrumentQC/) style website without needing to manually edit as many lines of code across separate .QMD files as currently required by following the [How-To-Tutorial](https://davidrach.github.io/InstrumentQC_Install/).

CytometryQC is a rather non-traditional R package. Namely, it's sole purpose is to write code tailored to your individual instrument computers, that can then be automated to process the QC data files present in a particular folder. CytometryQC also generates customized .qmd files that provide the stylistic elements that make up the InstrumentQC website after rendering. 

It also provides helper files to set up automated processing of the QC files at designated times of the day via Windows Taskscheduler; create the GitHub repositories, and run the core git commands needed to to ensure the processed data gets archived and is available for visualization by the website. 

As of early November 2025, we are nearing completion, wrapping up a couple bugs and implementing additional instruments. Please reach out to David if you are interested in getting assistance with setting up at your own institution, since each new location reveals a couple bugs we had not previously encountered in the last implementation. 

For those curious how this automated setup differs compared to the previously outline [How-To-Tutorial](https://davidrach.github.io/InstrumentQC_Install/), follow along for what will be the CytometryQC installation vignette once we complete debugging the current workflow.

Thanks!
David Rach

# Getting Set Up

## Context

All elements of our [InstrumentQC](https://umgccfcss.github.io/InstrumentQC/) website start off as individual code files within an InstrumentQC folder that is version-controled (tracked) by Git. All the contents of this folder work together to process the QC data, pass it to GitHub, and/or cobble together the Quarto website. 

As a result of this, generating an equivalent folder with the necessary components is the first step, while allowing for swapping in customized elements for the individual institution. 

To get started, go to your instrument's computer (ideally connected to instrument, see [offline](offline.qmd) for other options) and make sure required [software](https://davidrach.github.io/InstrumentQC_Install/Installation.html) is installed, and that [Git and Rstudio](https://davidrach.github.io/InstrumentQC_Install/GitAndRstudio.html#linking-rstudio-and-github) are communicating with each other. 

Once these steps are completed, we will install both the Luciernaga and CytometryQC packages from GitHub. 

## Installing Packages

```{r}
#| eval: FALSE

if(!require("remotes")) install.packages("remotes")

remotes::install_github("https://github.com/DavidRach/Luciernaga")

remotes::install_github("https://github.com/DavidRach/CytometryQC")
```

Once this is done, we will load CytometryQC via the library call

```{r}
library(CytometryQC)
```

## Folder Setup

Setting up the InstrumentQC folder is executed via the FolderSetup() function, the basic format can be seen below. 

```{r}
#| eval: FALSE
FolderSetup(organization_name="", organization_website="",
githubusername="", institution_name = "")
```

In the context of our institution setup, we have provided the customized elements by placing the values within the " " marks. As you are setting up equivalent for your institution, edit in as appropiate. 

```{r}
#| eval: FALSE
FolderSetup(
  SetUpGit = FALSE,
  organization_name = "UMGCC FCSS",
  organization_website = "https://www.medschool.umaryland.edu/cibr/core/umgccc_flow/",
  githubusername = "umgccfcss",
  institution_name = "University of Maryland, Baltimore"
)
```

Once you run enter, it should proceed to generate an initial InstrumentQC2 folder containing the necessary website framework components. 

# Adding Instruments

Next step is adding the instruments. Note, some of the code chunks in the .qmd and .R files are the previously mentioned things not ready before Cyto I need a couple weekends to work out, but the majority of the code works as intended, so if you want to edit these manually, reach out and I can walk through the locations. Or hurry up my editing. Either way :D 

We would run something like this for each Cytek instrument being added:

```{r}
#| eval: FALSE

AddInstruments(
  name="The5Laser",
  manufacturer = "Cytek",
  uv = 16,
  violet = 16,
  blue = 14,
  yellowgreen = 10,
  red = 8,
  TheFCSFolderPath = NULL,
  CytekbioExportFolderPath = NULL
)
```

This code would add all the required components to the existing InstrumentQC2 backbone to allow for the processing and rendering of the QC data. TheFCSFolderPath and CytekExportFolderPath arguments are in case the folders are different from traditional location after SpectroFlo installation on your individual computer. 

For the BD instruments, the process above is similar, but specifying FCS path argument the location of the .fcs QC files. 

For non-Cytek and non-BD instruments, option of adding is retained, as long as you know how the detector configuration is set up. I am interested in adding other spectral cytometry platforms in as I work out existing bugs, so reach out if you have one and are wanting to get it working on your eventual dashboard. 

After this is done, you could either add all other instruments right now while you are thinking about it, or wait until you are on their respective computers later when you can check the file path. 

# Render the Website

Having everything setup, we would now make sure the website can render, see how-to-tutorial for details while we are under development. 

# Push data to a new GitHub repository

We would create and move the data to a new repository on Github, see how-to-tutorial for details while we are under development.

# Repeat checks on other instruments

# Set task scheduler to run at time of your choice

# Ensure that the GitHub actions runs correctly to automatically render the website after QC data gets sent in the morning

# Generate the historical data repositories. 

Once the regular website is in working order, it is time to generate the historical elements. Basically, for each instrument present on the website, CytometryQC will produce an additional repository for, and then for every year of data, CytometryQC will need to create a webpage to visualize. Then these new webpages get linked in to the main website so that when you click, you automatically navigate over without realizing you made the switch.

To do so in the current workflow, you run the following:

```{r}
#| eval: FALSE
HistoricalPages(githubusername="", Archive="Bead")
```

With arguments provided being the githubusername to which to save the new repositories to, and whether to use Bead or Holistic format for referencing stored datasets. 

# Conclusion

This is the extent of what we are working on, stay tuned later this summer once everything gets completed. 

Best-
David